Translation of B Implementations to the LLVM: Specification

### 2014-03-02 DOCUMENTATION/specification.tex
Adding to TODO in specification.tex

B constants shall be translated to constants in the LLVM program. The
translation of scalar constants consists in substituting them with their value.
\DD{The translation of non-scalar constants will be defined in a next version of
  this document.}  The definition of the translation for expressions is
described next in section~\ref{sec:expr}.

@@

[[[ DEPRECATED ]]]

>>>>

B constants shall be translated to constants in the LLVM program. The
translation of scalar constants consists in substituting them with their value.
%TODO Look the following text. 
The translation of non-scalar constants will be defined in a next version of
this document. The definition of the translation for expressions is
described next in section~\ref{sec:expr}.

@@

%TODO It is deprecated 
%[[[TODO: DEPRECATED ]]]
